### 2021-03-15 sections/summary.tex
Update summary.tex

I am a PRS in the DPhil in Politics programme in the Department of Politics and International Relations and St Hilda’s College at the University of Oxford, United Kingdom. Furthermore, I am an Instructor in the Department of Public Administration and Policy at the Faculty of Economics and Management at the Universidad de Santiago, where I have been working since 2014.

Before starting the DPhil, I earned a BA (2:1) in Government and an MA (1st) in Political Science, both from the Universidad de Chile. Moreover, I worked as a lecturer at the Universidad de Santiago and the Universidad de Chile, as well as a consultant for the United Nations Development Programme.

My doctoral research is supervised by Professor Petra Schleiter at St Hilda’s College and focuses on the stability of cabinets in Latin American presidential democracies. My research is financially supported by the Chilean National Agency for Research and Development. Additionally, I am interested in the political elite’s socialisation, civil services, and crisis management.
\vspace{1mm}
\end{cvparagraph}

>>>>

I am completing my DPhil (PhD) dissertation in the Department of Politics and International Relations and St Hilda’s College at the University of Oxford, United Kingdom. I am currently based at Oxford, working on my research. Furthermore, I am an Instructor Professor in the Management and Public Policies Department at the Faculty of Administration and Economics at the Universidad de Santiago de Chile.

Before starting the DPhil, in October 2019, I earned an MA (1st) in Political Science and a BA (2:1) in Government, both from the Universidad de Chile. Moreover, I was a lecturer at the Universidad de Chile and a consultant for the United Nations Development Programme (UNDP).

My doctoral research is supervised by Professor Petra Schleiter and focuses on cabinets’ stability in Latin American presidential democracies. In my DPhil project, I combine the principal-agent theory elements to evaluate the actors’ incentives and strategies in presidential systems. My empirical strategy employs propensity scores and matching methods, competing risks models, and IV estimations. My research is funded by the Chilean National Agency for Research and Development.
\vspace{1mm}
\end{cvparagraph}
